Galois Transformers and Modular Abstract Interpreters

### 2015-03-26 writeup/oopsla2015.tex
final cut?

The design and implementation of static analyzers have becoming
increasingly systematic.  Yet for a given language or analysis
feature, it often requires tedious and error prone work to implement
an analyzer and prove it sound.
%
In short, static analysis features and their proofs of soundness do
not compose well, causing a dearth of reuse in both implementation and
metatheory.

@@

We solve the problem of systematically constructing static analyzers by
introducing \emph{Galois transformers}: monad transformers that
transport Galois connection properties.  In concert with a monadic
interpreter, we define a library of monad transformers that
implement building blocks for classic analysis parameters like context, path,
and heap (in)sensitivity. Moreover, these can be composed together 
% to realize a program analysis monad, 
\emph{independent of the language being analyzed}.

>>>>

The design and implementation of static analyzers has become increasingly
systematic.  Yet for a given language or analysis feature, it often requires
tedious and error prone work to implement an analyzer and prove it sound. In
short, static analysis features and their proofs of soundness do not compose
well, causing a dearth of reuse in both implementation and metatheory.

@@

We solve the problem of systematically constructing static analyzers by
introducing \emph{Galois transformers}: monad transformers that transport
Galois connection properties.  In concert with a monadic interpreter, we define
a library of monad transformers that implement building blocks for classic
analysis parameters like context, path, and heap (in)sensitivity. Moreover,
these can be composed together \emph{independent of the language being
analyzed}.
